30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
Completed conclusion and added some references

	\section{Tor vulnerabilities and attacks}
Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?]. In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, X attacks, Y attacks and Z attacks.

@@

@@

			\subsection{Bootstrapping new nodes}
		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with. In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
Moving this system to a non peer-to-peer base is difficult. Dingledine et al. stated that this indeed is still an open problem. With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network. Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.

@@

		From this table we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor. The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity or XXXXXX.\\

@@

	\appendices
%		\section{Proof of the First Zonklar Equation}
%			Appendix one text goes here.

			% you can choose not to have a title for an appendix
			% if you want by leaving the argument blank
%		\section{}
%			Appendix two text goes here.

		% use section* for acknowledgement
%		\section*{Acknowledgment}
%			The authors would like to thank...

		% Can use something like this to put references on a page
		% by themselves when using endfloat and the captionsoff option.
%		\ifCLASSOPTIONcaptionsoff
%		  \newpage
%		\fi

		% trigger a \newpage just before the given reference
		% number - used to balance the columns on the last page
		% adjust value as needed - may need to be readjusted if
		% the document is modified later
		%\IEEEtriggeratref{8}
		% The "triggered" command can be changed if desired:
		%\IEEEtriggercmd{\enlargethispage{-5in}}

		% references section

		% can use a bibliography generated by BibTeX as a .bbl file
		% BibTeX documentation can be easily obtained at:
		% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
		% The IEEEtran BibTeX style support page is at:
		% http://www.michaelshell.org/tex/ieeetran/bibtex/
		%\bibliographystyle{IEEEtran}
		% argument is your BibTeX string definitions and bibliography database(s)
		%\bibliography{IEEEabrv,../bib/paper}
		%
		% <OR> manually copy in the resultant .bbl file
		% set second argument of \begin to the number of references
		% (used to reserve space for the reference number labels box)
	\bibliography{paper_references}

>>>>

	\section{Tor vulnerabilities and attacks}
Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}. In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.

@@

		\subsection{Low-Resource Routing attacks}
		Hier wat over routing attacks

		\subsection{Sybil attacks}
		Hier wat over sybil attacks

		\subsection{Replay Attacks}
		Hier wat over replay attacks

@@

			\subsection{Bootstrapping new nodes}
		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with. In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.\\

Moving this system to a non peer-to-peer base is difficult. Dingledine et al. stated that this indeed is still an open problem. With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network. Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.

@@

		From this table we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor. The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of  attacks.\\

@@

	\appendices

	\bibliography{paper_references}
